HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2021-12-02 hermes_paper/hermes_paper.tex
Fixed bug in caption

\begin{table*}
  \caption{Fashion time series overview. For each couple geozone/category, we give the number of female and male trends (Female/Male)\\}
  \label{sample-table}
  \centering
  \resizebox{0.85\width}{!}{
  \begin{tabular}{l||lllllllll}
    %hline
    \\
    &  \textbf{Top}  & \textbf{Pants} & \textbf{Short} & \textbf{Skirt} & \textbf{Dress} & \textbf{Coat} & \textbf{Shoes} & \textbf{Color} & \textbf{Texture}  \\
    \hline
    \hline
    \\
\textbf{United States} & 411/208 & 149/112 & 47/22 & 29/- & 20/- & 208/151 & 293/86 & 38/44 & 85/81\\
     \textbf{Europe} & 409/228 &  134/114 & 48/21 & 28/- & 20/- & 211/159 & 303/78 & 41/42 & 87/74\\
     \textbf{Japan} &  403/218 & 136/107 & 49/31 & 28/- &  23/- & 185/149 &  311/78 & 46/42 &  92/65\\
     \textbf{China} &  424/202 & 147/114 & 46/29 & 27/- &  27/- & 178/161 &  310/78 & 41/47 &  88/77\\
     \textbf{Brazil} &  431/222 & 134/117 & 49/27 & 30/- &  28/- & 203/152 & 311/76 & 48/41 & 107/84\\
     \\
     %\hline
     \textbf{Total} & 2078/1078 & 700/564 & 239/130 & 142/- & 118/- & 985/772 & 1528/396 & 214/216 & 459/381\\
    %\hline
  \end{tabular}
  }
\end{table*}

@@

\begin{table*}
  \caption{Results summary on our 10000ts Fashion dataset. For each metric, we compute the average on all our time series. For our approaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.\\}
  \centering
  \resizebox{1.2\width}{!}{
  \begin{tabular}{l||llllllllll}
   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
    \hline
	\hline
	\rule{0pt}{2ex} \\
     \textit{snaive} && 0.881 & - && 25.27 & - && 1. & -\\
     \textit{thetam}  && 0.844 & - && 24.17 & - && 0.970 & -\\
     \textit{arima} && 0.826 & - && 23.63 & - && 0.949 & -\\
     \textit{ets} && 0.807 & - && 23.58 & - && 0.937 & -\\
     \textit{hermes-ets-ws} && 0.769 & 0.004 && 22.69 & 0.126 && 0.901 & 0.007\\
     \textit{stlm} && 0.770 & - && 22.05 & - && 0.882 & -\\
     \textit{hermes-ets} && 0.759 & 0.001 && 22.16 & 0.026 && 0.875 & 0.001\\
     \textit{tbats} && 0.745 & - && 21.13 & - && 0.850 & -\\
     \textit{lstm-ws} && 0.728 & 0.004 && 20.18 & 0.085 && 0.837 & 0.004\\
     \textit{lstm} && 0.724 & 0.003 && 20.08 & 0.052  && 0.825 & 0.004\\
     \textit{hermes-tbats-ws} && 0.713 & 0.005 && 20.53 & 0.170 && 0.825 & 0.009\\
     \textbf{\textit{hermes-tbats}} && \textbf{0.715} & 0.002 && \textbf{20.41} & 0.056 && \textbf{0.816} & 0.002\\
    %\hline
  \end{tabular}
  }
\label{tab:metricresults}
\end{table*}

@@

\begin{table*}
  \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series. For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.\\}
  \centering
  \resizebox{1.2\width}{!}{
  \begin{tabular}{l||llllllllll}
   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
    \hline
	\hline
	\rule{0pt}{2ex} \\
     \textit{snaive} && 0.871 & - && 25.29 & - && 1. & -\\
     \textit{thetam}  && 0.849 & - && 24.58 & - && 0.980 & -\\
     \textit{arima} && 0.821 & - && 23.69 & - && 0.951 & -\\
     \textit{ets} && 0.801 & - && 24.18 & - && 0.944 & -\\
     \textit{stlm} && 0.765 & - && 22.22 & - && 0.885 & -\\
     \textit{lstm-nows} && 0.740 & 0.007 && 20.56 & 0.154 && 0.856 & 0.008\\
     \textit{tbats} && 0.734 & - && 21.19 & - && 0.847 & -\\
     \textbf{\textit{hybrid-nows}} && \textbf{0.719} & 0.002 && \textbf{20.79} & 0.094 && \textbf{0.833} & 0.004\\
  \end{tabular}
  }
\label{tab:1000metricresults}
\end{table*}

%\begin{table*}
%  \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series. For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
%  \centering
%  \begin{tabular}{lllllll}
%    \hline
%    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
%    \hline
%     \textit{snaive} & 0.871 & - & 25.29 & - & 1. & -\\
%     \textit{thetam}  & 0.849 & - & 24.58 & - & 0.980 & -\\
%     \textit{arima} & 0.821 & - & 23.69 & - & 0.951 & -\\
%     \textit{ets} & 0.801 & - & 24.18 & - & 0.944 & -\\
%     \textit{hybrid-nows-ets} & 0.768 & 0.002 & 22.91 & 0.111 & 0.902 & 0.005\\
%     \textit{stlm} & 0.765 & - & 22.22 & - & 0.885 & -\\
%     \textit{lstm-nows} & 0.740 & 0.007 & 20.56 & 0.154 & 0.856 & 0.008\\
%     \textit{tbats} & 0.734 & - & 21.19 & - & 0.847 & -\\
%     \textit{hybrid-nows} & 0.719 & 0.002 & 20.79 & 0.094 & 0.833 & 0.004\\
%    \hline
%  \end{tabular}
%\label{tab:metricresults}
%\end{table*}
\begin{table*}
  \caption{Results summary on our 100ts Fashion dataset. For each metric, we compute the average on all our time series. For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.\\}
  \centering
  \resizebox{1.2\width}{!}{
  \begin{tabular}{l||llllllllll}
   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
    \hline
	\hline
	\rule{0pt}{2ex} \\
     \textit{snaive} && 0.876 & - && 26.98 & - && 1. & -\\
     \textit{thetam}  && 0.823 & - && 25.11 & - && 0.944 & -\\
     \textit{arima} && 0.814 & - && 24.61 & - && 0.940 & -\\
     \textit{lstm-nows} && 0.767 & 0.045 && 22.22 & 0.848 && 0.877 & 0.051\\
     \textit{stlm} && 0.742 & - && 23.03 & - & 0.863 & -\\
     \textit{tbats} && 0.745 & - && 22.16 & - & 0.856 & -\\
     \textbf{\textit{hybrid-nows}} && \textbf{0.739} & 0.003 && \textbf{22.31} & 0.083 && \textbf{0.845} & 0.003\\
  \end{tabular}
  }
\label{tab:100metricresults}
\end{table*}

>>>>

\begin{table*}
  \caption{Fashion time series overview. For each couple geozone/category, we give the number of female and male trends (Female/Male)}
  \label{sample-table}
  \centering
  \resizebox{0.85\width}{!}{
  \begin{tabular}{l||lllllllll}
    %hline
    \\
    &  \textbf{Top}  & \textbf{Pants} & \textbf{Short} & \textbf{Skirt} & \textbf{Dress} & \textbf{Coat} & \textbf{Shoes} & \textbf{Color} & \textbf{Texture}  \\
    \hline
    \hline
    \\
\textbf{United States} & 411/208 & 149/112 & 47/22 & 29/- & 20/- & 208/151 & 293/86 & 38/44 & 85/81\\
     \textbf{Europe} & 409/228 &  134/114 & 48/21 & 28/- & 20/- & 211/159 & 303/78 & 41/42 & 87/74\\
     \textbf{Japan} &  403/218 & 136/107 & 49/31 & 28/- &  23/- & 185/149 &  311/78 & 46/42 &  92/65\\
     \textbf{China} &  424/202 & 147/114 & 46/29 & 27/- &  27/- & 178/161 &  310/78 & 41/47 &  88/77\\
     \textbf{Brazil} &  431/222 & 134/117 & 49/27 & 30/- &  28/- & 203/152 & 311/76 & 48/41 & 107/84\\
     \\
     %\hline
     \textbf{Total} & 2078/1078 & 700/564 & 239/130 & 142/- & 118/- & 985/772 & 1528/396 & 214/216 & 459/381\\
    %\hline
  \end{tabular}
  }
\end{table*}

@@

\begin{table*}
  \caption{Results summary on our 10000ts Fashion dataset. For each metric, we compute the average on all our time series. For our approaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
  \centering
  \resizebox{1.2\width}{!}{
  \begin{tabular}{l||llllllllll}
   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
    \hline
	\hline
	\rule{0pt}{2ex} \\
     \textit{snaive} && 0.881 & - && 25.27 & - && 1. & -\\
     \textit{thetam}  && 0.844 & - && 24.17 & - && 0.970 & -\\
     \textit{arima} && 0.826 & - && 23.63 & - && 0.949 & -\\
     \textit{ets} && 0.807 & - && 23.58 & - && 0.937 & -\\
     \textit{hermes-ets-ws} && 0.769 & 0.004 && 22.69 & 0.126 && 0.901 & 0.007\\
     \textit{stlm} && 0.770 & - && 22.05 & - && 0.882 & -\\
     \textit{hermes-ets} && 0.759 & 0.001 && 22.16 & 0.026 && 0.875 & 0.001\\
     \textit{tbats} && 0.745 & - && 21.13 & - && 0.850 & -\\
     \textit{lstm-ws} && 0.728 & 0.004 && 20.18 & 0.085 && 0.837 & 0.004\\
     \textit{lstm} && 0.724 & 0.003 && 20.08 & 0.052  && 0.825 & 0.004\\
     \textit{hermes-tbats-ws} && 0.713 & 0.005 && 20.53 & 0.170 && 0.825 & 0.009\\
     \textbf{\textit{hermes-tbats}} && \textbf{0.715} & 0.002 && \textbf{20.41} & 0.056 && \textbf{0.816} & 0.002\\
    %\hline
  \end{tabular}
  }
\label{tab:metricresults}
\end{table*}

@@

\begin{table*}
  \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series. For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
  \centering
  \resizebox{1.2\width}{!}{
  \begin{tabular}{l||llllllllll}
   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
    \hline
	\hline
	\rule{0pt}{2ex} \\
     \textit{snaive} && 0.871 & - && 25.29 & - && 1. & -\\
     \textit{thetam}  && 0.849 & - && 24.58 & - && 0.980 & -\\
     \textit{arima} && 0.821 & - && 23.69 & - && 0.951 & -\\
     \textit{ets} && 0.801 & - && 24.18 & - && 0.944 & -\\
     \textit{stlm} && 0.765 & - && 22.22 & - && 0.885 & -\\
     \textit{lstm-nows} && 0.740 & 0.007 && 20.56 & 0.154 && 0.856 & 0.008\\
     \textit{tbats} && 0.734 & - && 21.19 & - && 0.847 & -\\
     \textbf{\textit{hybrid-nows}} && \textbf{0.719} & 0.002 && \textbf{20.79} & 0.094 && \textbf{0.833} & 0.004\\
  \end{tabular}
  }
\label{tab:1000metricresults}
\end{table*}

%\begin{table*}
%  \caption{Results summary on our 1000ts Fashion dataset.For each metric, we compute the average on all our time series. For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
%  \centering
%  \begin{tabular}{lllllll}
%    \hline
%    &  MASE-mean  & MASE-std & SMAPE-mean & SMAPE-std & OWA-mean & OWA-std  \\
%    \hline
%     \textit{snaive} & 0.871 & - & 25.29 & - & 1. & -\\
%     \textit{thetam}  & 0.849 & - & 24.58 & - & 0.980 & -\\
%     \textit{arima} & 0.821 & - & 23.69 & - & 0.951 & -\\
%     \textit{ets} & 0.801 & - & 24.18 & - & 0.944 & -\\
%     \textit{hybrid-nows-ets} & 0.768 & 0.002 & 22.91 & 0.111 & 0.902 & 0.005\\
%     \textit{stlm} & 0.765 & - & 22.22 & - & 0.885 & -\\
%     \textit{lstm-nows} & 0.740 & 0.007 & 20.56 & 0.154 & 0.856 & 0.008\\
%     \textit{tbats} & 0.734 & - & 21.19 & - & 0.847 & -\\
%     \textit{hybrid-nows} & 0.719 & 0.002 & 20.79 & 0.094 & 0.833 & 0.004\\
%    \hline
%  \end{tabular}
%\label{tab:metricresults}
%\end{table*}
\begin{table*}
  \caption{Results summary on our 100ts Fashion dataset. For each metric, we compute the average on all our time series. For our two apporaches using neural network, we trained 10 models with different seeds and we display the mean and the standard deviation of our 10 results.}
  \centering
  \resizebox{1.2\width}{!}{
  \begin{tabular}{l||llllllllll}
   &&\multicolumn{2}{c}{\textbf{MASE}} && \multicolumn{2}{c}{\textbf{SMAPE}} && \multicolumn{2}{c}{\textbf{M4}}& \\
    &&  \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} && \textit{mean}  & \textit{std} \\
    \hline
	\hline
	\rule{0pt}{2ex} \\
     \textit{snaive} && 0.876 & - && 26.98 & - && 1. & -\\
     \textit{thetam}  && 0.823 & - && 25.11 & - && 0.944 & -\\
     \textit{arima} && 0.814 & - && 24.61 & - && 0.940 & -\\
     \textit{lstm-nows} && 0.767 & 0.045 && 22.22 & 0.848 && 0.877 & 0.051\\
     \textit{stlm} && 0.742 & - && 23.03 & - & 0.863 & -\\
     \textit{tbats} && 0.745 & - && 22.16 & - & 0.856 & -\\
     \textbf{\textit{hybrid-nows}} && \textbf{0.739} & 0.003 && \textbf{22.31} & 0.083 && \textbf{0.845} & 0.003\\
  \end{tabular}
  }
\label{tab:100metricresults}
\end{table*}
